Doublet splitting of fusion alpha-particle driven ion cyclotron emission

### 2022-02-26 manuscript.tex
title change, refs names fixup

\title[]{Doublet splitting and linear amplitude characteristics of fusion alpha-particle driven ion cyclotron emission}

@@

\bibitem{Dendy1995}
Dendy R O, McClements K G, Lashmore-Davies C, Cottrell G A, Majeski R, and Cauffman S 1995 \textit{Nucl. Fusion} \textbf{35} 1733–1742
%  , “Ion cyclotron emission due to collective instability of fusion prod-ucts and beam ions in TFTR and JET,”

@@

\bibitem{Cottrell1993} 
Cottrell G A, Bhatnagar V, Costa O D, Dendy R O, Jacquinot J, McClements K G, McCune D, Nave M, Smeulders P, and Start D 1993 \textit{Nucl. Fusion} \textbf{33}, 31365–1387
% 
% "Ion cyclotron emission measurements during JET deuterium-tritium experiments,"

@@

\bibitem{Ichimura2008}
Ichimura M, Higaki H, Kakimoto S, Yamaguchi Y, Nemoto K, Katano M, Ishikawa M, Moriyama S, and Suzuki T 2008 \textit{Nucl. Fusion} \textbf{48}, 035012
% , "Observation of spontaneously excited waves in the ion cyclotron frequency range on JT-60u,"

@@

\bibitem{Chapman2017}
Chapman B, Dendy R O, McClements K, Chapman S C, Yun G, Thatipamula S, and Kim M 2017 \textit{Nucl. Fusion} \textbf{57} 124004
% , "Sub-microsecond temporal evolution of edge density during edge localized modes in KSTAR tokamak plasmas inferred from ion cyclotron emission,"

\bibitem{Chapman2018}
Chapman B, Dendy R O, Chapman S C, McClements K G, Yun G S and Thatipamula S G 2018 \textit{Nucl. Fusion} \textbf{58} 096027

@@

\bibitem{McClements1996}
McClements K G, Dendy R O, Lashmore-Davies C N, Cottrell G A, Cauffman S and Majeski R (1996) \textit{Phys. Plasmas} \textbf{3} 543

@@

\bibitem{Reman2019}
Reman B, Dendy R O, Akiyama T, Chapman S C, Cook J W S, Igami  H, Inagaki S, Saito K, and Yun G, 2019 \textit{Nucl. Fusion} \textbf{59} 096013
% “Interpreting observations of ion cyclotron emission from large helical device plasmas with beam-injected ion populations,”

@@

\bibitem{Sharapov2014}
Sharapov S E , Lilley M K, Akers R, Ayed N B, Cecconello M, Cook J W S, Cunningham G, and Verwichte E 2014 \textit{Phys. Plasmas} \textbf{21} 082501
% , "Bi-directional Alfvén cyclotron instabilities in the mega-amp spherical tokamak"

@@

\bibitem{Heidbrink2006}
Heidbrink W W, Fredrickson E, Gorelenkov N N, Rhodes T, Zeeland  M A 2006 \textit{Nucl. Fusion} \textbf{46} 324
% Observation of compressional Alfvén eigenmodes (CAE) in a conventional tokamak.

@@

\bibitem{Fredrickson2019}
Fredrickson E D, Gorelenkov  N N, Bell R E, Diallo A, LeBlanc B P, Podestà  M, and NSTX Team 2019 \textit{Physics of Plasmas} \textbf{26}, 032111
% "Emission in the ion cyclotron range of frequencies (ICE) on NSTX and NSTX-U",

>>>>

\title[]{Doublet splitting of fusion alpha-particle driven ion cyclotron emission}

@@

\bibitem{Dendy1995}
Dendy R O {\textit et al} 1995 \textit{Nucl. Fusion} \textbf{35} 1733–1742
%Dendy R O, McClements K G, Lashmore-Davies C, Cottrell G A, Majeski R, and Cauffman S 1995 \textit{Nucl. Fusion} \textbf{35} 1733–1742
%  , “Ion cyclotron emission due to collective instability of fusion prod-ucts and beam ions in TFTR and JET,”

@@

\bibitem{Cottrell1993} 
Cottrell G A {\textit et al} 1993 \textit{Nucl. Fusion} \textbf{33}, 31365–1387
%Cottrell G A, Bhatnagar V, Costa O D, Dendy R O, Jacquinot J, McClements K G, McCune D, Nave M, Smeulders P, and Start D 1993 \textit{Nucl. Fusion} \textbf{33}, 31365–1387
% 
% "Ion cyclotron emission measurements during JET deuterium-tritium experiments,"

@@

\bibitem{Ichimura2008}
Ichimura M {\textit et al} 2008 \textit{Nucl. Fusion} \textbf{48}, 035012
%Ichimura M, Higaki H, Kakimoto S, Yamaguchi Y, Nemoto K, Katano M, Ishikawa M, Moriyama S, and Suzuki T 2008 \textit{Nucl. Fusion} \textbf{48}, 035012
% , "Observation of spontaneously excited waves in the ion cyclotron frequency range on JT-60u,"

@@

\bibitem{Chapman2017}
Chapman B {\textit et al} 2017 \textit{Nucl. Fusion} \textbf{57} 124004
%Chapman B, Dendy R O, McClements K, Chapman S C, Yun G, Thatipamula S, and Kim M 2017 \textit{Nucl. Fusion} \textbf{57} 124004
% , "Sub-microsecond temporal evolution of edge density during edge localized modes in KSTAR tokamak plasmas inferred from ion cyclotron emission,"

\bibitem{Chapman2018}
Chapman B {\textit et al} 2018 \textit{Nucl. Fusion} \textbf{58} 096027
%Chapman B, Dendy R O, Chapman S C, McClements K G, Yun G S and Thatipamula S G 2018 \textit{Nucl. Fusion} \textbf{58} 096027

@@

\bibitem{McClements1996}
McClements K G {\textit et al} 1996 \textit{Phys. Plasmas} \textbf{3} 543
%McClements K G, Dendy R O, Lashmore-Davies C N, Cottrell G A, Cauffman S and Majeski R (1996) \textit{Phys. Plasmas} \textbf{3} 543

@@

\bibitem{Reman2019}
Reman B {\textit et al} 2019 \textit{Nucl. Fusion} \textbf{59} 096013
%Reman B, Dendy R O, Akiyama T, Chapman S C, Cook J W S, Igami  H, Inagaki S, Saito K, and Yun G, 2019 \textit{Nucl. Fusion} \textbf{59} 096013
% “Interpreting observations of ion cyclotron emission from large helical device plasmas with beam-injected ion populations,”

@@

\bibitem{Sharapov2014}
Sharapov S E {\textit et al} 2014 \textit{Phys. Plasmas} \textbf{21} 082501
%Sharapov S E, Lilley M K, Akers R, Ayed N B, Cecconello M, Cook J W S, Cunningham G, and Verwichte E 2014 \textit{Phys. Plasmas} \textbf{21} 082501
% , "Bi-directional Alfvén cyclotron instabilities in the mega-amp spherical tokamak"

@@

\bibitem{Heidbrink2006}
Heidbrink W W {\textit et al} A 2006 \textit{Nucl. Fusion} \textbf{46} 324
%Heidbrink W W, Fredrickson E, Gorelenkov N N, Rhodes T, Zeeland M A 2006 \textit{Nucl. Fusion} \textbf{46} 324
% Observation of compressional Alfvén eigenmodes (CAE) in a conventional tokamak.

@@

\bibitem{Fredrickson2019}
Fredrickson E D {\textit et al} 2019 \textit{Physics of Plasmas} \textbf{26}, 032111
%Fredrickson E D, Gorelenkov  N N, Bell R E, Diallo A, LeBlanc B P, Podestà  M, and NSTX Team 2019 \textit{Physics of Plasmas} \textbf{26}, 032111
% "Emission in the ion cyclotron range of frequencies (ICE) on NSTX and NSTX-U",
